### 2024-07-22 NN/tables/backward.tex
commit

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                                                                                           &    R2 \\
\hline
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2'] & 82.69 \\
 ['conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 62.45 \\
 ['flow\_rate1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 81.63 \\
 ['flow\_rate1', 'conc\_nano1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']            & 73.64 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 72.94 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']          & 67.45 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 68.03 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 76.57 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'heat\_flux2', 'X\_D2']            & 38.28 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'X\_D2']                & 69.39 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2']          & 81.61 \\
\hline
\end{tabular}
            \caption{Results of Backward Feature Elimination}
            \label{table-backward}
        \end{table*}

>>>>

    \begin{table*}
        \centering
        \begin{tabular}{p{12cm}r}r}
\hline
\hline
 features                                                                                            &    R2 \\
\hline
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 84.97 \\
 conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.27 \\
 flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.9  \\
 flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 73.44 \\
 flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 74.25 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 70.58 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.67 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 40.24 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 49.33 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 72.42 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 74.5  \\
\hline
\end{tabular}
\hline
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}
